---
title: "07 Modeling - Simple Linear Regression"
date: "`r Sys.Date()`"
institute: "Numeric Mind"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Task1

Load the sales dataset from your data folder assign it to variable 'budget'.

```{r}
library(tidyverse)

budget <- read_csv("./data/sales.csv")

budget

```


## Task2

Lets look at the relationship between advertisement budget and sales.

```{r}

ggplot(data =    ,
       mapping = aes(x=advertisement_budget, y= sales))  
  
```

## Task3

Check for outliers [univariate]

Hint : you can use box plot:geom_boxplot() to see if there are any outliers

```{r}

ggplot(data=budget, aes(y=sales)) + 

```

## Task 4

Another method to check if there are any outliers.

```{r}
# install.packagaes(rstatix)

library(rstatix)

identify_outliers(data = budget, variable = "sales")

is_outlier(budget$sales)
is_extreme(budget$sales)
```


## Task 5

Remove outliers

```{r}
budget <- budget %>% filter(is_outlier(sales)==F)

budget
```

## Task 6

Again visualize your dataset for outliers using box plot.

```{r}

ggplot(data = budget, mapping= aes(y= sales)) + 

```

## Task 7
Create a linear regression model to predict sales based on advertisement_budget.

```{r}

# install.packages("MASS")
library(MASS)

#Linear model for predicting values of Sales based on Advertisement_budget.

model1<- lm(sales~advertisement_budget, data=budget)

summary(model1)

```
## Task 8
Regression plot

```{r}
# Plot of linear model.

ggplot(data=budget, aes(x=advertisement_budget, y= sales))+
  geom_point() +
  geom_smooth(method='lm', se=F)
```

## Task 9
Predict Sales for new dataset

```{r}

# Create a new dataset
new_ad_budget <- data.frame(advertisement_budget= c(100, 1000, 10000, 100000))
new_ad_budget

predict.lm(model1, new_ad_budget)
```


